Bioverse: Origins of Life

### 2024-03-06 src/tex/ms.tex
include powergrid figure

>>>>

We now investigate the sensitivity of the achieved statistical power of our default transit survey to the a priori unconstrained threshold \gls{NUV} flux $F_\mathrm{NUV, min}$ and the abiogenesis rate $f_\mathrm{life}$.
Figure~\ref{fig:powergrid} shows the statistical power as a function of these parameters for a sample size of $N=\var{N_nautilus}$.
Higher values of $F_\mathrm{NUV, min}$ increase the achieved statistical power of the survey, as the dataset under the alternative hypothesis $H_3$ differs more from the null hypothesis with increasing threshold flux.
The same is true for the abiogenesis rate $f_\mathrm{life}$, where higher values increase the evidence for $H_3$.

\begin{figure}
    \script{powergrid.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/powergrid.pdf}
        \caption{Statistical power as a function of threshold \gls{NUV} flux and abiogenesis rate. For a given sample size (here: $N=\var{N_nautilus}$), the achieved statistical power of the survey is enhanced for higher values of $F_\mathrm{NUV, min}$ and $f_\mathrm{life}$.}
        \label{fig:powergrid}
    \end{centering}
\end{figure}
